---
title: "HW1 - Tidy Tuesday"
author: "Gabriella Nieves"
format: html
editor: visual
---

```{r include = FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
```

# Carbon Emissions Dataset

```{r echo= FALSE}
emissions <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2024/2024-05-21/emissions.csv')
head(emissions)
```


## Total Production of Natural Gas From 1854 to 2023 in Billion Cubic Feet/Year by Company (greater than 10,000 BCF/Yr)
```{r plot-wider, fig.height=50, echo=FALSE}
emissions_gas_production <- emissions %>%
  group_by(parent_entity, commodity) %>%
  summarize(sum = sum(production_value), .groups = "keep") %>%
  filter(commodity == "Natural Gas") %>%
  arrange(sum) %>%
  filter(sum > 10000)

emissions_gas_production %>%
  ggplot(aes(x = sum, y = reorder(parent_entity, -sum))) +
  geom_col(fill = "magenta4") +
  labs(
    x = "Average Billion Cubic Feet of Natural Gas",
    y = "Company",
    title = ""
  ) +
  theme_minimal()
```

### The top three companies in natural gas production are ExxonMobil, the Former Soviet Union, and Gazprom. ExxonMobil is seen to have around 200 trillion cubic feet of natural gas production. The Former Soviet Union has produced around 300 trillion cubic feet of natural gas producion. Gazprom almost doubles the Former Soviet Union with around 700 trillion cubic feet of natural gas produced. 
